---
name: Jacob Rozran
position: "Data Professional"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: www.jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(VennDiagram)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Summary

\btwocol
I am a data professional who has real-world experience putting data products 
into production. I am curious and constantly learning and improving - staying up 
to date with trends in all facets of the data science lifecycle. 

I love to learn in general, but mostly I am a data fanatic. I love reading, 
writing, and learning about all things data science, analysis, and 
visualizations. Give me data and I will provide insight. 

\begin{center}

```{r, out.width = "60%"}
venn.plot <- draw.triple.venn(
        area1 = 65,
        area2 = 75,
        area3 = 85,
        n12 = 35,
        n23 = 15,
        n13 = 25,
        n123 = 5,
        category = c("Data Skills", "Statistics", "Project Managment"),
        fill = c("#1d6ae5", "#b3c5e0", "#19396b"),
        cat.cex = 1.5,
        cat.col = c("#1d6ae5", "#b3c5e0", "#19396b"),
        cex = c(0, 0, 0, 0, 0, 0, 0)
)
```

\end{center}

\etwocol

# Data Science Skills

\begin{center}

```{r, results = "asis"}
df <- data.frame(a = c("Machine Learning", "Feature Creation", "Process Automation", 
                       "Regression Analysis", "Data Visualization"),
                 b = c("RStudio", "Jupyter Notebooks", "Tableau", "Splunk",
                       "Excel"),
                 c = c("R", "Python", "Bash", "SAS", ""),
                 d = c("Hive/Impala (Hadoop)", "MySQL", "Oracle", "MongoDB", 
                       "Neo4J"))

names(df) <- c("METHODS", "APPLICATIONS", "LANGUAGES", "DATABASES")

kable(df, row.names = FALSE, "latex", booktabs = T)
```
\end{center}

# Experience
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Lead and manage the data analytics and engineering team for Xfinity Mobile Credit Risk Management, including hiring and training of staff analysts and engineers, collaborating with and providing analysis for stakeholders, and tracking and prioritizing all team tasking.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Designed and built a fraud decision making tool that combines custom feature creation, statistical and business rules, and predictive models built in R, Python, and Bash, which, in large part, is responsible for a decrease in month-over-month fraud losses by 92% in 2018.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Forecast involuntary churn (both bad debt and unit loss) for the organization on the numerous segments of our customer base.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Built and maintain numerous Tableau and Splunk dashboards representing fraud and credit to the organization.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Provide coaching, leadership, and mentorship to all analysts on the Xfinity Mobile Risk Management team."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Designed and built predictive models, which improved compromised user account detection times and discovery accuracy – this work was presented internally along with several internal blog posts about the effort.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Used statistical methods to discover and automate the detection of anomalies.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Created forecasts of user base growth and project completion.",
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Maintained and monitored KPIs for multiple application teams within the organization."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Served as a Project Manager and ScrumMaster for the Messaging Application Engineering (MAE) team, responsible for Residential Voicemail and Email Engineering teams.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Obtained my Project Management Professional (PMP) and Certified ScrumMaster (CSM) certifications.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Instituted and evangelized Scrum on both the email and voicemail teams, migrating from a hybrid of waterfall and Kanban, which led to higher team productivity, better communication across teams from development through deployment to production, and improved interaction with our product owners.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Managed the scheduling and owned the priorities for multiple work streams and teams."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

\makecvfooter{`r format(Sys.time(), '%B %Y')`}{Jacob Rozran}{1}
\newpage 

# Experience (Continued)
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Implementation Manager", "NCS Main Study Information Management Systems Project (Booz Allen Hamilton)", "Rockville, MD", "Nov 2010 - Apr 2013", "Served as the Implementation Manager and Site Administrator for the National Children’s Study (NCS) Portal, a Microsoft SharePoint 2010 web application, the NCS Application Homepage, and NCS Password Self Service.",
        "Implementation Manager", "NCS Main Study Information Management Systems Project (Booz Allen Hamilton)", "Rockville, MD", "Nov 2010 - Apr 2013", "Developed a configuration change process for the NCS Portal that streamlined the enhancement process for the site and provided the client with quicker updates while still meeting contractual and firm guidelines."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Financial Analyst/Project Manager", "NAVAIR RIS Project (Booz Allen Hamilton)", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Developed a financial tracking system for client, which allowed key stakeholders to view current and projected funding over the lifetime of the contract.",
        "Financial Analyst/Project Manager", "NAVAIR RIS Project (Booz Allen Hamilton)", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Tracked current funding for multiple engineers and monitored the expenditures of funds on their contracts, which ensured that projects remained on budget."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Volunteer
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Assisted Montgomery County Public Defender to define an analytics strategy to support competitive salaries and fair defence for all Montgomery County residents.",
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Created, built, and maintained advanced analysis."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Education
```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Masters of Science - Applied Statistics", "Villanova University", "Villanova, PA", "2015 - 2017", "Completed my program while working full time"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```

```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative for Student Lobbying Day in Harrisburg, PA, 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Traditions Council Treasurer, 2007 - 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Dean’s List, 2006, 2008",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative to Colonial Athletic Association's Student Athlete Advisory Committee, 2006",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Varsity Soccer Player, 2004 - 2006"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```


\makecvfooter{`r format(Sys.time(), '%B %Y')`}{Jacob Rozran}{2}

