---
name: Jacob Rozran
position: "Data Scientist/Data Analyst/Data Engineer"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: +1 410 231 9371
www: www.jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
twitter: rozran00
github: jrozra200
linkedin: jacob-rozran-884580b
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

<!-- # Professional Goal -->

<!-- GOAL TEXT WOULD GO HERE -->

# Skills

## Data Science

* Tree-based machine learning, bootstrap sampling, forecasting, feature creation, process automation, regression analysis, data visualization, advanced analytics

## Applications

* RStudio, Jupyter Notebooks, Excel, Tableau, Splunk

## Languages

* R, Python, Bash, SAS

## Databases

* Hive/Impala (Hadoop), MySQL, Oracle, MongoDB, Neo4J, Teradata

# Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Manager of Data Analytics", "Comcast", "Philadelphia, PA", "Mar 2017 - Present", "Lead and manage the data analytics and engineering team for Xfinity Mobile Credit Risk Management, including hiring and training of staff analysts and engineers, collaborating with and providing analysis for stakeholders, and tracking and prioritizing all team tasking.",
  "Manager of Data Analytics", "Comcast", "Philadelphia, PA", "Mar 2017 - Present", "Designed and built a fraud decision making tool that combines custom feature creation, statistical and business rules, and predictive models built in R, Python, and Bash, which, in large part, is responsible for a decrease in month-over-month fraud losses by 92% in 2018.",
  "Manager of Data Analytics", "Comcast", "Philadelphia, PA", "Mar 2017 - Present", "Forecast involuntary churn (both bad debt and unit loss) for the organization on the numerous segments of our customer base.",
  "Manager of Data Analytics", "Comcast", "Philadelphia, PA", "Mar 2017 - Present", "Built and maintain numerous Tableau and Splunk dashboards representing fraud and credit to the organization.",
  "Manager of Data Analytics", "Comcast", "Philadelphia, PA", "Mar 2017 - Present", "Provide coaching, leadership, and mentorship to all analysts on the Xfinity Mobile Risk Management team.",
  "Senior Data Analyst", "Comcast", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Designed and built predictive models, which improved compromised user account detection times and discovery accuracy, for the Internet Services Engineering Analytics team – this work was presented internally along with several internal blog posts about the effort.", 
  "Senior Data Analyst", "Comcast", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Used statistical methods to discover and automate the detection of anomalies.", 
  "Senior Data Analyst", "Comcast", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Created forecasts of user base growth and project completion.", 
  "Project Manager", "Comcast", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Served as a Project Manager and ScrumMaster for the Messaging Application Engineering (MAE) team, responsible for Residential Voicemail and Email Engineering teams.",
  "Project Manager", "Comcast", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Obtained my Project Management Professional (PMP) and Certified ScrumMaster (CSM) certifications during my tenure as PM for the Messaging team.",
  "Implementation Manager", "Booz Allen Hamilton", "Rockville, MD", "Nov 2010 - Apr 2013", "Served as the Implementation Manager and Site Administrator for the National Children’s Study (NCS) Portal, a Microsoft SharePoint 2010 web application, the NCS Application Homepage, and NCS Password Self Service.",
  "Financial Analyst/Project Manager", "Booz Allen Hamilton", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Developed a financial tracking system for client, which allowed key stakeholders to view current and projected funding over the lifetime of the contract."
 ) %>% 
  detailed_entries(role, dates, company, loc, details)
```


# Education
```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates,
  "MS, Applied Statistics", "Villanova University", "Villanova, PA", "2015 - 2017",
  "BS, Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009"
) %>% 
  detailed_entries(degree, dates, uni, loc)
```

