---
name: Jacob Rozran
position: "Leader | Fixer | Builder | Helper | Learner | Connector"
address: "1400 Maryland Ave. Havertown, PA 19083"
phone: (410) 231-9371
www: www.jakelearnsdatascience.com
email: "jacob.rozran@gmail.com"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(VennDiagram)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Summary

\btwocol
I am a multifaceted professional who excels at leading teams, fixing problems, 
building products, creating and maintaining relationships, and helping customers 
through excellent service. I am curious and constantly learning and improving. 

I love to investigate the status quo - always looking to see if there are better 
ways to solve challenges. I am also a technophile, interested in enhancing our 
world with more and more sophisticated techologies. 

\begin{center}

```{r, out.width = "75%"}
venn.plot <- draw.triple.venn(
        area1 = 65,
        area2 = 75,
        area3 = 85,
        n12 = 35,
        n23 = 15,
        n13 = 25,
        n123 = 5,
        category = c("Leadership", "Relationship    \nManagement    ", 
                     "Customer Service"),
        fill = c("#1d6ae5", "#b3c5e0", "#19396b"),
        cat.cex = 1.5,
        cat.col = c("#1d6ae5", "#b3c5e0", "#19396b"),
        cex = c(0, 0, 0, 0, 0, 0, 0)
)
```

\end{center}

\etwocol

# Experience
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Lead and manage the data analytics and engineering team for Xfinity Mobile Credit Risk Management, including hiring and training of staff analysts and engineers, collaborating with and providing analysis for stakeholders, and tracking and prioritizing all team tasking.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Build and maintain relationships across the organization - our decisions, though data driven, are nothing without the understanding and buy-in from our partners in Product, Marketing, Finance, Care, Logistics, and Project Management.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Provide coaching, leadership, and mentorship to all analysts on the Xfinity Mobile Risk Management team.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Designed and built a fraud decision making tool that is responsible for a decrease in month-over-month fraud losses by 92% in 2018.",
        "Manager of Data Analytics", "Xfinity Mobile Risk Management (Comcast)", "Philadelphia, PA", "Mar 2017 - Present", "Forecast involuntary churn (both bad debt and unit loss) for the organization on the numerous segments of our customer base."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Led a team of analysts responsible for detecting and investigating anomalies in the Xfinity Connect email platform - always striving to improve the customer experience.",
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Designed and built predictive models, which improved compromised user account detection times and discovery accuracy.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Used statistical methods to discover and automate the detection of anomalies.", 
        "Senior Data Analyst", "Internet Services Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Created forecasts of user base growth and project completion."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Served as a Project Manager and ScrumMaster for the Messaging Application Engineering (MAE) team.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Managed the scheduling and owned the priorities for multiple work streams and teams.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Instituted and evangelized Scrum on both the email and voicemail teams, which led to higher team productivity, better communication across teams from development through deployment to production, and improved interaction with our product owners.",
        "Project Manager", "Messaging Application Engineering (Comcast)", "Philadelphia, PA", "Sep 2014 - Mar 2017", "Obtained my Project Management Professional (PMP) and Certified ScrumMaster (CSM) certifications."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Implementation Manager", "NCS Main Study Information Management Systems Project (Booz Allen Hamilton)", "Rockville, MD", "Nov 2010 - Apr 2013", "Served as the Implementation Manager and Site Administrator for the National Children’s Study (NCS) Portal, a Microsoft SharePoint 2010 web application, the NCS Application Homepage, and NCS Password Self Service.",
        "Implementation Manager", "NCS Main Study Information Management Systems Project (Booz Allen Hamilton)", "Rockville, MD", "Nov 2010 - Apr 2013", "Developed a configuration change process for the NCS Portal that streamlined the enhancement process for the site and provided the client with quicker updates while still meeting contractual and firm guidelines."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Financial Analyst/Project Manager", "NAVAIR RIS Project (Booz Allen Hamilton)", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Developed a financial tracking system for client, which allowed key stakeholders to view current and projected funding over the lifetime of the contract.",
        "Financial Analyst/Project Manager", "NAVAIR RIS Project (Booz Allen Hamilton)", "Lexington Park, MD", "Nov 2009 - Oct 2010", "Tracked current funding for multiple engineers and monitored the expenditures of funds on their contracts, which ensured that projects remained on budget."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

\makecvfooter{`r format(Sys.time(), '%B %Y')`}{Jacob Rozran}{1}
\newpage 

# Experience (Continued)

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Assistant, Customized Project Development", "Greater Philadelphia Chamber of Commerce", "Philadelphia, PA", "Apr 2007 - June 2009", "Managed the Young Professionals Network (YPN), an affiliate of the Chamber with over 1,100 members, which saw a growth in membership of more than 35% over tenure.",
        "Assistant, Customized Project Development", "Greater Philadelphia Chamber of Commerce", "Philadelphia, PA", "Apr 2007 - June 2009", "Created and managed the social networking presence for YPN.",
        "Assistant, Customized Project Development", "Greater Philadelphia Chamber of Commerce", "Philadelphia, PA", "Apr 2007 - June 2009", "Coordinated and planned the monthly YPN networking events and the yearly YPN Golf Outing."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Barista", "Starbucks Coffee Company", "MD & PA", "June 2003 - Apr 2007", "Provided legenday customer service, accurately handled till & took customer orders, and crafted amazing beverages."
        ) %>% detailed_entries(role, dates, company, loc, details)
```


# Volunteer
```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Organizer", "Data Jawn Conference", "Philadelphia, PA", "April 2019 - Present", "Assisted in promotion, speaker selection, and day-of-event logistics for the Data Jawn, a Philadelphia data conference highlighting the great work of our local data commnuity."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

```{r}
tribble(
        ~ role, ~ company, ~ loc, ~ dates, ~ details,
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Assisted Montgomery County Public Defender to define an analytics strategy to support competitive salaries and fair defence for all Montgomery County residents.",
        "Data Analyst", "Montgomery County Public Defender", "Norristown, PA", "May 2016 - Jun 2017", "Created, built, and maintained advanced analysis."
        ) %>% detailed_entries(role, dates, company, loc, details)
```

# Education
```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Masters of Science - Applied Statistics", "Villanova University", "Villanova, PA", "2015 - 2017", "Completed my program while working full time"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```

```{r}
tribble(
        ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative for Student Lobbying Day in Harrisburg, PA, 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Traditions Council Treasurer, 2007 - 2009",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Dean’s List, 2006, 2008",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel Representative to Colonial Athletic Association's Student Athlete Advisory Committee, 2006",
        "Bachelors of Science - Business & Engineering", "Drexel University", "Philadelphia, PA", "2004 - 2009", "Drexel University Varsity Soccer Player, 2004 - 2006"
        ) %>% detailed_entries(degree, dates, uni, loc, details)
```


\makecvfooter{`r format(Sys.time(), '%B %Y')`}{Jacob Rozran}{2}

